---
title: "README !"
output: rmarkdown::github_document
---

# Super-Bowl-Ads

# Usage and examples of project_utils package

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
#devtools::install_github("pmassicotte/gtrendsR", force=TRUE)
library(gtrendsR)
source("project_utils.R")
```

import the datasets:

```{r}
data <- get_data() # the main dataset, contains ads info
rating <- get_rating_data() # contains rating info, e.g., ads cost, viewrs and etc
general <- get_general_data() # ads categories, e.g., beer, car and etc 
```

-   <code>search_dates</code>

    returns the dates where a brand had ads on the Superbowl

```{r}
brand <- "Coca-Cola"
dates <- search_dates(brand)
head(dates)
```

-   <code>search_brands</code>

    returns the brands that had a Superbowl ad on the desired year

```{r}
brands <- search_brands(2015)
brands
```

-   gtopics(brands, time)

    Works just like <code>gtrends</code> (from gtrendsR library) but shows the results for the brand's topic

    ```{r message=FALSE, paged.print=TRUE}
    head(gtopics("Doritos","all"))
    ```

-   <code>gtopics_plot(brands, date, rday=1)</code>

    Will display the google trends plot, where rday is the "radius" of days before and after the ad the you with to observe so following the examples above:

```{r}
gtopics_plot(brands=brand, date=dates[2,], rday=1)
gtopics_plot(brands=brand, date=dates[2,], rday=3)
```

\*The dashed line marks the Superbowl date

If we want to compare several brands together we can use gtrend_plot as follows:

```{r}
brands_to_compare <- brands[1:3,]$brand # taking 3 companies from the exmaple above (Budweiser, Coca-Cola, Doritos)
gtopics_plot(brands=brands_to_compare, date=dates[2,], rday=1)
gtopics_plot(brands=brands_to_compare, date=dates[2,], rday=7)
```

-   <code>gtopics_r(brands, date, rday=1)</code>

    Returns the "RAW" tabular data of gtrends (while converting the brand name to the relevant topic)

```{r}
gtopics_r(brands=brands_to_compare, date=dates[2,], rday=1)
```
